One page description

### 2016-12-08 publications/Journal/4-performance.tex
* updated all images * fixed broken citations with incorrect capitalization

Second, the \textit{Interconnect} model, a merge of PHold~\cite{PHold} and the \textit{HI} model of DEVStone~\cite{DEVStone}, creates $n$ atomic models, where each model has exactly one output port.
Similar to PHold, all models are connected to one another, but all through the same port: every atomic model receives each generated event (\textit{i.e.}, the event is broadcasted).
The model takes one parameter: the number of atomic models.
This benchmark shows the complexity of event creation, event routing, and simultaneous event handling.
An example for three atomic models is shown in Figure~\ref{fig:interconnect_model}.

Third, the \textit{PHold} model~\cite{PHold}, creates $n$ atomic models, where each atomic model has exactly $n-1$ output ports.
Each atomic model is directly connected to every other atomic model.
After a random delay, an atomic model sends out an event to a randomly selected output port.
Output port selection happens in two phases: first it is decided whether the event should be sent within the same kernel, or outside of the kernel.
Afterwards, a uniform selection is made between the possible atomic models.
The model takes two parameters: the percentage of remote events (determining the percentage of events routed to other kernels), and the percentage of high-priority events.
High-priority events are events generated in a very short time after the previous event.
This benchmark shows how the simulation kernel behaves in the presence of many local or remote events, in combination with a varying percentage of high-priority events.
An example for four atomic models, split over two kernels, is shown in Figure~\ref{fig:PHold_model}.

>>>>

Second, the \textit{Interconnect} model, a merge of PHold~\cite{PHOLD} and the \textit{HI} model of DEVStone~\cite{DEVStone}, creates $n$ atomic models, where each model has exactly one output port.
Similar to PHold, all models are connected to one another, but all through the same port: every atomic model receives each generated event (\textit{i.e.}, the event is broadcasted).
The model takes one parameter: the number of atomic models.
This benchmark shows the complexity of event creation, event routing, and simultaneous event handling.
An example for three atomic models is shown in Figure~\ref{fig:interconnect_model}.

Third, the \textit{PHold} model~\cite{PHOLD}, creates $n$ atomic models, where each atomic model has exactly $n-1$ output ports.
Each atomic model is directly connected to every other atomic model.
After a random delay, an atomic model sends out an event to a randomly selected output port.
Output port selection happens in two phases: first it is decided whether the event should be sent within the same kernel, or outside of the kernel.
Afterwards, a uniform selection is made between the possible atomic models.
The model takes two parameters: the percentage of remote events (determining the percentage of events routed to other kernels), and the percentage of high-priority events.
High-priority events are events generated in a very short time after the previous event.
This benchmark shows how the simulation kernel behaves in the presence of many local or remote events, in combination with a varying percentage of high-priority events.
An example for four atomic models, split over two kernels, is shown in Figure~\ref{fig:PHold_model}.
